\section{Exploratory Data Analysis}
\label{sec:eda}

The provided dataset contains personal information of several people
(8164 samples), such as date of birth and current employment and maps
it to the observation if the person became unemployed in the next 12 months.

The dataset was made available without any information about it's contents
except for the property names.
Each one was analysed for insights and anomalies.

The following list details what could be obtained exploring the data
(column name, value types and values).

\begin{description}
\item [id] Integer, identifier for each subject, all values distinct no
    problems detected.

\item [target] Integer, did the subject become unemployed in the following
    12 months.

\item [birth date] Date (YYYY-MM-DD), date of birth of the subject.
    The youngest being \DTMdisplaydate{2016}{2}{10}{-1} and the oldest
    \DTMdisplaydate{1928}{01}{09}{-1}.
    Frequency plot (see \vref{fig:birth_date_freq}) shows nothing surprising.

\item [country of origin] Categorical, country names come in a variety of
    inconsistent formats.

\item [domestic relationship type] Categorical,
    (see \vref{tab:domestic_relationship_type_value_counts}) who the subject
    lives with.
    Categories are unclear and ill defined.
    Moreover it is inconsistent with the \emph{domestic status}, there are a
    considerable number of entries classified as
    \emph{domestic relation type}--\emph{never married} and
    \emph{domestic status}--\emph{d} (presumably divorced)
    (see \vref{tab:domestic_type_by_status_counts}).

\item [domestic status] Categorical, marital status or if has married several
    times (see \vref{tab:domestic_status_value_counts}).
    By elimination category \emph{d} is supposedly divorced.

\item [earned dividends] Numerical, monetary amount (currency not specified).
    Return from distribution of corporate earnings, it's 0 for all samples.

\item [ethnicity] Categorical, categories have funny names
    (see \vref{tab:ethnicity_value_counts}).

\item [gender] Categorical, all female dataset
    (see \vref{tab:gender_value_counts}).

\item [job type] Categorical, current job type of the subject
    (see \vref{tab:job_type_value_counts}), government, self employed,
    item etc\ldots

\item [interest earned] Numerical, monetary amount (currency not specified).
    Returns from loaning money (see \vref{fig:interest_earned_freq}).

\item [monthly work] Numerical, number of hours of work per month
    (see \vref{fig:monthly_work_freq})

\item [profession] Categorical, type of profession
    (see \vref{tab:profession_value_counts}).

\item [school level] Categorical, subject level of schooling
    (see \vref{tab:school_level_value_counts}).

\end{description}

